Generating Images From Captions\\ With Attention

### 2015-11-01 iclr-paper-new.tex
a

\section{Model}
\label{sec:model}
Our proposed model 
defines a generative process of images conditioned on captions. In particular, captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on a canvas $c_t$ over time $t=1,...,T$. Our model can be viewed as a part of the sequence-to-sequence framework \citep{ilya_mt,cho_mt,nitish_video}.
%Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

@@

The terms in the variational lower bound are rearranged using the law of total expectation. Therefore, the objective function $\loss$ is calculated as follows:
\begin{align}
\label{eq:loss}
\loss =  &\expectation_{Q(\Lat_{1:T}\given\icaption,\oimage)}\left[ \log p(\oimage\given\icaption,\Lat_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\Lat_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\Lat_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The expectation can be approximated by $\numSamples$ Monte Carlo samples $\LatSample_{1:T}$ from $\post(\Lat_{1:T}\given\icaption, \oimage)$:
\begin{align}
\label{eq:loss_mc}
\loss \approx  &\frac{1}{\numSamples}\sum_{\sampleIdx=1}^\numSamples\left[ \log p(\oimage\given\icaption,\LatSample^\sampleIdx_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
In all of our experiments, we used only a single sample 
from $\post(\Lat_{1:T}\given\icaption, \oimage)$ during training.

>>>>

\section{AlignDRAW Model}
\label{sec:model}
Our proposed model 
defines a generative process of images conditioned on captions. In particular, captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on a canvas $c_t$ over time $t=1,...,T$. The model can be viewed as a part of the sequence-to-sequence framework \citep{ilya_mt,cho_mt,nitish_video}.
%Our proposed model can be viewed as a part of sequence-to-sequence framework \citep{ilya_mt}, \citep{cho_mt}, \citep{nitish_video} where captions are represented as a sequence of consecutive words and images are represented as a sequence of patches drawn on canvas over time $t=1,...,T$. Let $\icaption$ be the input caption, consisting of $N$ words $y_{1}, y_{2}, ..., y_{n}$ and $\oimage$ be the image corresponding to that caption.

@@

The terms in the variational lower bound can be rearranged using the law of total expectation. Therefore, the variational bound $\loss$ is calculated as follows:
\begin{align}
\label{eq:loss}
\loss =  &\expectation_{Q(\Lat_{1:T}\given\icaption,\oimage)}\left[ \log p(\oimage\given\icaption,\Lat_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\Lat_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\Lat_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The expectation can be approximated by $\numSamples$ Monte Carlo samples $\LatSample_{1:T}$ from $\post(\Lat_{1:T}\given\icaption, \oimage)$:
\begin{align}
\label{eq:loss_mc}
\loss \approx  &\frac{1}{\numSamples}\sum_{\sampleIdx=1}^\numSamples\left[ \log p(\oimage\given\icaption,\LatSample^\sampleIdx_{1:T}) - \sum_{t=2}^T\kldiv\left(\post(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption,\oimage)\klBars\prior(\Lat_t\given\LatSample^\sampleIdx_{1:t-1},\icaption)\right) \right] \nonumber \\& - \kldiv\left(\post(\Lat_1\given\oimage)\klBars\prior(\Lat_1)\right).
\end{align}
The model can be trained using stochastic gradient descent. 
In all of our experiments, we used only a single sample 
from $\post(\Lat_{1:T}\given\icaption, \oimage)$ for parameter learning.
Training details, hyperparameter settings,
and the overall model architecture are specified in Appendix. 
We will also release our code with pretrained models.
